---
title: "teeth"
author: "blwang3"
date: "2020-09-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

```{r import-teeth}
teeth <- read.csv('data/teeth.csv', row.names = 1)
head(teeth)
```

```{r boxplots}
boxplot(len ~ dose, data = teeth)
boxplot(len ~ supp, data = teeth)
boxplot(len ~ dose + supp, data = teeth)
```

```{r permute tooth length}
# Observed differences in teeth length due to supplement method
mean(teeth$len[teeth$supp =='OJ']) - mean(teeth$len[teeth$supp == 'VC'])
supp_perm <- sample(teeth$supp)
mean(teeth$len[supp_perm == 'OJ']) - mean(teeth$len[supp_perm == 'VC'])
```

wflow_publish("analysis/teeth.Rmd", message = "Analyze teeth growth")
#commits teeth.Rmd changes to html
#wflow_status checks the rest of your files for commits (published), so now publish them as well using the same publish command
#publish basically tells git to store snapshots of these files, a publish/commit can be returned to in the future 

wflow_use_github("blwang3")
#connects this project to your github

wflow_publish(republish = TRUE)
#adds a few convenient links that will work nicely with github, can run this step earlier in the process too

wflow_git_push()
#pushes your changes to your github that you just linked
#Now we want to make sure our new pushed github repository looks like a nice website - go to settings, scroll down to GitHub pages, change settings to 'master' and 'docs' and SAVE. Then scroll back down and click on the URL and you should be directed to your website!

